Examining FDR correction issue in clusterProfiler - RNA-seq example

### 2024-06-05 analysis/analyse_rnaseq1.Rmd
titles

---
title: "Examining background gene lists in clusterProfiler - RNA-seq example"
author: "Mark Ziemann & Anusuiya Bora"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 7
    fig_height: 7
theme: cosmo
---

>>>>

---
title: "Examining background gene list issue in clusterProfiler - RNA-seq example"
author: "Mark Ziemann & Anusuiya Bora"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 7
    fig_height: 7
theme: cosmo
---

### 2024-06-05 analysis/analyse_rnaseq2.Rmd
update figs
titles

---
title: "Examining background gene lists in clusterProfiler - RNA-seq example"
author: "Mark Ziemann & Anusuiya Bora"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 7
    fig_height: 7
theme: cosmo
---

@@

# overall
oa <- matrix(paste(res1$nsig_bad,res1$nsig_good,signif(res1$jaccard,2)),ncol=9)
rownames(oa) <- names(d)
colnames(oa) <- names(gs)

>>>>

---
title: "Examining FDR correction issue in clusterProfiler - RNA-seq example"
author: "Mark Ziemann & Anusuiya Bora"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 7
    fig_height: 7
theme: cosmo
---

@@

# overall
oa <- matrix(paste(res1$nsig_bad,res1$nsig_good,signif(res1$Jaccard,2)),ncol=9)
rownames(oa) <- names(d)
colnames(oa) <- names(gs)
